%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Work Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
\cventry
{Software Developper} % Job title
{Burkett Statistical Consulting} % Organization
{Remote - Ottawa, ON} % Location
{May. 2024 - Aug. 2024} % Date(s)
{
  \begin{cvitems} % Description(s) of tasks/responsibilities
    \item {Applied \textbf{Simulated Annealing Search} to optimize scheduling problems. Improved the metrics by approximately \textbf{20\%} by reducing the search space, improving neighbor selection, and tuning cost function.}
    \item {Built an automatic CI pipeline that benchmarks the performance of the algorithm using \textbf{GitHub Actions}.}
    \item {Developed machine learning models in \textbf{R} in forecasting and classification tasks, achieving positive skill scores in comparison to the baseline model.}
  \end{cvitems}
}

%---------------------------------------------------------
\cventry
{Automation} % Job title
{Friendlier} % Organization
{Guelph, ON} % Location
{Sep. 2023 - Dec. 2023} % Date(s)
{
  \begin{cvitems} % Description(s) of tasks/responsibilities
    \item {Fully designed an automated solution that scans and sorts various types of containers, using a Raspberry Pi, a barcode scanner, servo motors and conveyor belts.}
    \item {Independently implemented a functional iteration of the design, replacing the original manual sorting process and increased the throughput from \textbf{300} unit per hour to \textbf{750} unit per hour.}
    \item {Developped a concurrent model in \textbf{Python} to handle IO, scheduler and data fetching in parallel, applying the producer-consumer pattern to communicate between threads.}
    \item {Automate operation logging and data collection, and designed a pipeline to generate reports and visualizations, using \textbf{Google Scripts.}}
  \end{cvitems}
}

%---------------------------------------------------------
  \cventry
    {Software Developper} % Job title
    {Data2Discovery} % Organization
    {Remote - Bloomington, US} % Location
    {Feb. 2023 - May. 2023} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Maintained and developed a data visualization dashboard using the \textbf{Dash} library.}
        \item {Patched design flaws, leveraged proper usage of the \textbf{Dash} library, and eliminated linearly increasing request time.}
        \item {Researched on the \textbf{Transformer model}, and hosted workshops discussing its internal workings and limitations.}
        \item {Lead projects among three data science graduate teams, contributed to decision making and organized regular internal communications.}
      \end{cvitems}
    }

%---------------------------------------------------------
\end{cventries}
