%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Projects}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Java, Spigot, SQLite, Maven} % Affiliation/role
    {\href{https://github.com/shiqui/simple-teleport}{SimpleTeleport {\faLink}}} % Organization/group
    {} % Location
    {2023} % Date(s)
    {
      \begin{cvitems} % Description(s) of experience/contributions/knowledge
        \item {Developed a Spigot plugin for Minecraft 1.20, managing home, warp and player teleports while keeping the experience as vanilla as possible.}
        \item {Implemented a SQLite database through JDBC to handle data storage.}
        \item {Added custom teleport animation with sound effects, potion effects, particle effects and animated bossbar.}
        \item {Published on SpigotMC, with currently 73 downloads after a month of release.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
  {Python, PyTorch} % Affiliation/role
  {\href{https://github.com/shiqui/PoetryGPT}{PoetryGPT {\faLink}}} % Organization/group
  {} % Location
  {2023} % Date(s)
  {
    \begin{cvitems} % Description(s) of experience/contributions/knowledge
      \item {Built a decoder only transformer model in PyTorch that generates Chinese Poems.}
      \item {Trained the model on a dataset of 10000 poems, using a character level tokenizer.}
    \end{cvitems}
  }

%---------------------------------------------------------
  \cventry
    {Python, Pygame, PyTorch} % Affiliation/role
    {\href{https://github.com/shiqui/TSDP-Reinforcement-Learning-in-Video-Games}{Reinforcement Learning in 2D Shooter {\faLink}}} % Organization/group
    {} % Location
    {2022} % Date(s)
    {
      \begin{cvitems} % Description(s) of experience/contributions/knowledge
        \item {Created a 2D top-down arena shooter game in PyGame with custom sprites and collision logics.}
        \item {Worked as a team to implemented Q learning with PyTorch and trained an AI that shoots moving targets in the game.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Python, Pygame} % Affiliation/role
    {\href{https://devpost.com/software/star-formation}{Star Formation Simulation: Astro Award Winner {\faLink}}} % Organization/group
    {Mcgill Physics Hackathon} % Location
    {2022} % Date(s)
    {
      \begin{cvitems} % Description(s) of experience/contributions/knowledge
        \item {Created a simulation of planetary motion in PyGame, demonstrating gravitational pulls between stars and the formation of larger bodies.}
        \item {Calculated the trajectories using Euler's method, based on physics simulated using Newton's Laws.}
        \item {Winner of Astro Award over 100+ participants in the McGill Physics Hackathon. }
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Python, TypeScript} % Affiliation/role
    {\href{https://devpost.com/software/svi-scheduler}{SVI Scheduler {\faLink}}} % Organization/group
    {MariHacks 2.0 - Hackathon} % Location
    {2021} % Date(s)
    {
      \begin{cvitems} % Description(s) of experience/contributions/knowledge
        \item {Developed a Google Sheet plugin that automatically balances work load across different workers based on their availabilities, using greedy algorithm and priority queue.}
        % \item {Deployed at a translation service for allophone patients, and is proven to be highly functional through worker feedbacks.}
      \end{cvitems}
    }

%---------------------------------------------------------
\end{cventries}
